Excuse me, do you have a moment to talk about version control?

### 2017-05-18 README.Rmd
Intro tweaks

Benefits of using hosted version control in your statistical practice:

  * Doing your work becomes tightly integrated with organizing, recording, and disseminating it. It's not a separate, burdensome task you are tempted to neglect.
  * The marginal effort required to create a web presence for a project is negligible.
  * GitHub makes a fantastic course management system for courses that use R. You and your students can exchange actual working code and explore the associated results.
  * By using common mechanics across work modes (research, teaching, analysis), you achieve basic competence quickly and avoid the demoralizing forget-relearn cycle.

@@

[Git](http://git-scm.com) is a __version control system__. Its original purpose was to help groups of developers work collaboratively on big software projects. Git manages the evolution of a set of files -- called a __repository__ -- in a sane, highly structured way. It is a bit like the "Track Changes" feature from Microsoft Word, but more rigorous, powerful, and scaled up to multiple files.

>>>>

There many benefits of using hosted version control in your statistical practice:

  * Doing your work becomes tightly integrated with organizing, recording, and disseminating it. It's not a separate, burdensome task you are tempted to neglect.
  * Collaboration becomes much more structured, with powerful tools for asynchronous work and managing versions.
  * The marginal effort required to create a web presence for a project is negligible.
  * GitHub makes a fantastic course management system for courses that use R. You and your students can exchange actual working code and explore the associated results.
  * By using common mechanics across work modes (research, teaching, analysis), you achieve basic competence quickly and avoid the demoralizing forget-relearn cycle.

@@

[Git](http://git-scm.com) is a __version control system__. Its original purpose was to help groups of developers work collaboratively on big software projects. Git manages the evolution of a set of files -- called a __repository__ or __repo__ -- in a sane, highly structured way. It is a bit like the "Track Changes" feature from Microsoft Word, but more rigorous, powerful, and scaled up to multiple files.
